---
title: "Replication File"
author: "Mark G. Sheppard"
---

```{r setup, include=FALSE}
# LOAD PACKAGES
if(!require(tidyverse)){install.packages("tidyverse", dependencies = TRUE); library(tidyverse, quietly = TRUE)}
if(!require(rstudioapi)){install.packages("rstudioapi", dependencies = TRUE); library(rstudioapi, quietly = TRUE)}

# IMPORT PACKAGES FOR PYTHON
if(!require(reticulate)){install.packages("reticulate", dependencies = TRUE); library(reticulate, quietly = TRUE)}

# IMPORT PACKAGES FOR STRUCTURAL BREAKS 
if(!require(zoo)){install.packages("zoo", dependencies = TRUE); library(zoo, quietly = TRUE)}
if(!require(sandwich)){install.packages("sandwich", dependencies = TRUE); library(sandwich, quietly = TRUE)}
if(!require(strucchange)){install.packages("strucchange", dependencies = TRUE); library(strucchange, quietly = TRUE)}
if(!require(readxl)){install.packages("readxl", dependencies = TRUE); library(readxl, quietly = TRUE)}

# IMPORT FRED API PACKAGES 
if(!require(fredr)){install.packages("fredr", dependencies = TRUE); library(fredr, quietly = TRUE)}
fredr_set_key("6352ad3b393d3ab83709630e61d2b14e")

#CLEAR CONSOLE
cat("\014")
```

```{r}
# DOWNLOAD PYTHON PACKAGES INTO R
conda_install(packages = "requests")
conda_install(packages = "pandas")
conda_install(packages = "numpy")
conda_install(packages = "time")
conda_install(packages = "urllib3")
```

## This Loads Packages in a Python Enviroment Within R-Studio
Since R and Python share a similar base language, the following code will allow you to load packages in Python within the R enviroment.

```{python, include=FALSE}
# IMPORT PACKAGES FOR PYTHON
import requests
import os
import pandas as pd
import numpy as np
import urllib
import time
```

## This Establishes The Directory for Navigation 
This code will create a folder with three separate sub-folders. Changing the below strings will alter the name of the folders and location of the folders. This folder will then be made into the working directory

```{r directory, include=FALSE}
##### CHNGE FOR PC #####



# SET DIRECTORY WITH NAMES OF FOLDERS
directory <- list("~/Desktop", "/Replication", "/Results", "/Code", "/Data")

#CLEAR CONSOLE
cat("\014")
```

## Creates Sub-Directory, Copies Current File, Renames/Relocates Code in Folder
Creates Sub-Directory, Copies Current File, Renames/Relocates Code in Folder

```{r pressure, echo=FALSE, include=FALSE}
# EXTRACT CURRENT FILENAME
filename <-gsub(".*/","",documentPath()) # Extracts filename 

# DELETE OLD WORK
unlink(paste(directory[1],directory[2],sep=""), recursive = TRUE)

#CREATES BASE DIRECTORY
dir.create(paste(directory[1],directory[2],sep=""))

#CREATES SUB DIRECTORY
dir.create(paste(directory[1],directory[2],directory[3],sep=""))
dir.create(paste(directory[1],directory[2],directory[4],sep=""))
dir.create(paste(directory[1],directory[2],directory[5],sep=""))

# MOVE FILE TO DIRECTORY
file.copy(from = filename, 
          to = paste(directory[1],directory[2],directory[4],"/",sep=""))

# RENAME CODE FILE
file.rename(from = paste(directory[1],directory[2],directory[4], "/", filename, sep=""), 
            to = paste(directory[1],directory[2],directory[4],"/", "code.Rmd",sep=""))

# CLEAR ENVIROMENT
#rm(directory, filename)

# CLEAR CONSOLE
cat("\014")
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

```{python, include=FALSE}
# Calculate Time to Source Data
start = time.time()

# Source Data
psz_url = 'http://gabriel-zucman.eu/files/PSZ2018MainData.xlsx'
as_url = 'http://davidsplinter.com/AutenSplinter-IncomeIneq.xlsx'
urllib.request.urlretrieve(psz_url, "piketty-saez-zucman.xlsx")
urllib.request.urlretrieve(as_url, "auten-splinter.xlsx")

# Print the Time Required to Source Data
end = time.time()
print("Downloading the data required", (end - start), "seconds.")
```

```{r, include=FALSE}
# MOVE FILE TO DIRECTORY
file.copy(from = "auten-splinter.xlsx", 
          to = paste(directory[1],directory[2],directory[5],"/",sep=""))

# MOVE FILE TO DIRECTORY
file.copy(from = "piketty-saez-zucman.xlsx", 
          to = paste(directory[1],directory[2],directory[5],"/",sep=""))
```

```{python, include=FALSE}
# Calculate Time to Download Data
start_ = time.time()

# Clean Data and Store as Pandas Object
psz_df = pd.read_excel(psz_url, 'Data', usecols=('A:AN, AQ:BJ, BM:CY, DB:EO, EQ:FY, GA:GN, GQ:HD, HG:HR, HT:IM, IO:IP, IS:JE, JG:JO'), header=[2]).drop([0,1]).rename(columns={"Series": "Year"})
psz_df.drop(psz_df.tail(11).index,inplace=True)
as_df = pd.read_excel(as_url, 'F-A1', header=[32], usecols=('A:E, G:J')).rename(columns={'Unnamed: 0': "Year"}).drop([56,57])

# Print the Time Required to Download Data
end_ = time.time()
print("Cleaning the data required", (end_ - start_), "seconds.")  
```

```{python, include=FALSE}
# Merge the Data
df = psz_df.merge(as_df, how='outer')
print("Merge complete") 
```

```{r, include=FALSE}
# Store Python Object as a R Object
df_full <- as.vector(py$df) # Saves Python Object as R
df_full <- df_full[1:102,] # Cuts off last observations
```

```{r, include=FALSE}
# Subset the Data
df <- df_full %>% 
  rename("value"= `Memo: Top 10% fiscal income per tax unit, incl. KG`, 
         "time" = Year) %>%
  select(time, value) %>% 
  filter(!is.na(value)) %>% 
  mutate(value = value*100) #Represent Decimals as Whole Numbers
```

```{r, include=FALSE}
# Source Tax Data from FRED, with API 
tax <- fredr(series_id = "IITTRHB",observation_start = as.Date("1913-01-01"),
             observation_end = as.Date("2014-01-01"), frequency = "a")
```

```{r, include=FALSE}
# Define 2 Break Points in Tax Data
bp_tax <- breakpoints(tax$value ~ 1, breaks = 2)

# Define 2 Break Points in Inequality Data
bp <- breakpoints(df$value ~ 1, breaks = 2)

# Alternatively To Set No Amount of Breaks
# bp <- breakpoints(df$value ~ 1)

# Unlist the Data
df$time <- unlist(df$time)

# PLot The Data
tax_plot <- ggplot(df, aes(x = unlist(time), y = value, group = 1)) +
  # Plot Data
  geom_line(color="#00B2D9") +
  # Color of Main Line"R Working File/test.xlsx"
  ggtitle("Top 10% Income Share") +
  xlab("Year") + 
  ylab("Income Share in Percentage") +
  # Labels
  theme_minimal() +
  # Basic Theme
  scale_x_discrete(labels = pretty(df$time, n = 15)) +
  # X Axis Tick Amount
  theme(axis.text.y = element_text(angle=0, size=7)) +
  # Axis Font Size and Angles
  theme(axis.text.x = element_text(angle=90, hjust=1, size=7),
        panel.grid.major.x = element_blank(),
        panel.grid.major.y = element_line(linetype = "dotted"), 
        panel.grid.minor.y = element_line(linetype = "dotted")) +
  # Add Note
  annotate("text", x = 1960, y = 36, label = "Postwar Era", vjust = -0.5, size=3, col = 'dark grey') +
  # Plot Structural Breaks
  geom_vline(data = tibble(breakpoints = df$time[bp$breakpoints]), 
             aes(xintercept = breakpoints), linetype='dotted', col = '#00809C') +
  geom_vline(data = tibble(breakpoints = df$time[bp_tax$breakpoints + 4]), #Added a lead of 4 Years
             aes(xintercept = breakpoints), col = '#858585', linetype='solid') +
  geom_hline(yintercept = 30, size = .1) +
  scale_x_yearqtr(format = "%Y") 

```


```{r}
# PRINT GRAPH
tax_plot

# SAVE PLOT IN RESULTS FOLDER
ggsave(paste(directory[1],directory[2],directory[3],"/", "tax_plot.pdf",sep=""), 
       width = 7, height = 4)
```

```{r, warning=FALSE}
# LOAD PACKAGES
if(!require(stargazer)){install.packages("stargazer", dependencies = TRUE); library(stargazer, quietly = TRUE)}; cat("\014")

# CREATE NEW VARIABLES
df_full$`Log of Top 1%` <- log(df_full$`Top 1% pre-tax share equal-split`)
df_full$`Log of Top 0.1%` <- log(df_full$`Top 0.1% pre-tax equal split`)

#RUN AND SAVE REGRESSION
homework_one_model_one <- lm(df_full$`Log of Top 1%` ~ tax$value)
homework_one_model_two <- lm(df_full$`Log of Top 0.1%` ~ tax$value)

#PRINT WITH STARGAZER
stargazer::stargazer(homework_one_model_one, homework_one_model_two, type="text", 
                     rownames = TRUE, covariate.labels=c("Tax Rate on Upper Incomes")); cat("\014")

# PRINT SINGLE VALUE
matrix_coef <- summary(homework_one_model_one)$coefficients
matrix_coef[2, 1]
```


